pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-01-24 article.tex
Introduction

Phylogenies are commonly used to explore evolutionary hypotheses.

@@

\verb;pirouette;'s documentation is extensive. All functions are documented
in the package's internal documentation. For quick use, 
each exported function shows a minimal example. 
For easy exploration, each exported function's documentation links to related functions.
Additionally, \verb;pirouette; has a vignette that demonstrates extensively how
to use it. There is documentation on the GitHub to get started, 
with a dozen examples of BEAUti screenshots with equivalent \verb;pirouette; code.
Finally, \verb;pirouette; has tutorial videos that can 
be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU} \giovanni{be sure that shortened link are not deprecated after a certain time}.

>>>>

Phylogenies are commonly used to explore evolutionary hypotheses.
The mode of diversification is one such hypothesis.
Phylogenies constructed from DNA alignments are commonly fit to
diversification models, or the other way around. For example,
[Etienne & Rosindell 2012] fit four bird phylogenies to the protracted
diversification model.

There are plenty of diversification models: constant-birth [Yule, 19..],
birth-death [Nee et al., 19..], time-dependent [?], diversity 
dependent [Etienne & ?, approx 2012], protracted 
birth-death [Rosindell & Etienne, 2011][Etienne & Rosindell, 2012],
multiple-birth death [Laudanno, Bilderbeek & Etienne, in preparation],
a rate shifting birth-death model [the SLS model. Laudanno & Etienne, in preparation]
punctuated equilibrium aka early burst [?Harmon],
dependent on a binary trait [BISSE model, ?Maddison], 
continuous trait [HISSE model],
concealed state [?MUSSE] or a combination of all [secSSE model, Leonel].

Diversification models are getting more complex over time. There are many
reasons for this. One reason is the increase in computing power,
allowing this heightened complexity to be possible.
Another reason is to explore a process that is not
yet captured by the other diversification models. An example of this
is the multiple-birth model [Laudanno, Bilderbeek & Etienne, in preparation], 
that is the first model to allow speciation to co-occur.

@@

\verb;pirouette;'s documentation is extensive. All functions are documented
in the package's internal documentation. For quick use, 
each exported function shows a minimal example. 
For easy exploration, each exported function's documentation links to related functions.
Additionally, \verb;pirouette; has a vignette that demonstrates extensively how
to use it.
